---
title: "Psych Tools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Psych Tools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
This package helps you clean raw psychology survey data and create APA-style plots for research papers.

# Loading the package and data
First, we load the package and the built-in toy dataset (survey_demo).

```{r setup}
library(project)
data(survey_demo)
head(survey_demo)
```

# 1. Scaling Likert Responses
We scale the 1-5 Likert responses for satisfaction and stress into a 0 to 1 range.

```{r}
survey_demo$satisfaction_scaled <- scale_responses(survey_demo$satisfaction)
survey_demo$stress_scaled <- scale_responses(survey_demo$stress)
```

# 2. Working with Keyword Tags
We split the comma-separated keyword tags from the open-ended responses into a clean list.
```{r}
kw <- split_keywords(survey_demo$tags)
str(kw)
```

# 3. Creating APA-style Plots
We create a scatter plot with the scaled scores and apply our custom APA theme.
```{r, fig.width=6, fig.height=4}
library(ggplot2)
ggplot(survey_demo, aes(x = satisfaction_scaled, y = stress_scaled)) +
  geom_point(size = 3, alpha = 0.7) +
  labs(title = "Satisfaction vs Stress", x = "Scaled Satisfaction", y = "Scaled Stress") +
  theme_apa()
```
